Galaxy Zoo: Morphological Classifications for 150,000 Galaxies in HST Legacy Imaging

### 2016-05-19 writeup/gz_hubble_data.tex
Streamline Section 6 intro. Closes #130.

The intended purpose of the GZH catalog is to provide a simple, yet flexible,
means of identifying samples of galaxies with a desired morphological type.
This section provides instructions for creating such samples using the vote
fractions corresponding to the tasks shown in Figure~\ref{fig:decisiontree}. We
stress that the selection process will vary based on the particular science
case. More conservative cuts can be applied to create pure, but not necessarily
complete, samples. These are useful for selecting galaxies exhibiting unique
morphologies for individual case studies or observing proposals. Looser cuts
can be applied to obtain samples with a higher level of completeness, which
will increase the sample size but can potentially decrease purity. Population
studies would make use of such large samples, in which statistical significance
is a crucial factor in evaluating results. \citet{mas11c,mel14,che15}, and
\citet{gal15} are examples of Galaxy~Zoo papers which select morphologies in this way.

In GZH, participants answered questions about a galaxy's morphology in a decision
tree format. With this structure, questions shown to a classifier were dependent on
their answers to the previous questions (Section~\ref{ssec:interface}).
Figure~\ref{fig:decisiontree} shows the possible paths available for answering
the questions offered in GZH. The colors represent the tier level of Tasks,
which indicate the number of previous Tasks the given Task is dependent upon.
The arm-number question, Task~11, is a 5$^\mathrm{th}$-tier Task, meaning that
whether this question is seen by a classifier was dependent on four Tasks preceding
it. In this case, it as only shown to classifiers who identified the galaxy as
featured/disk-shaped in Task~01, not clumpy in Task~12, not edge-on in Task~02,
and having spiral structure in Task~10.

>>>>

The primary purpose of the GZH catalog is to provide a reliable method of
selecting galaxies of a desired morphological type.  This section provides
instructions for creating such samples using the vote fractions corresponding
to the tasks shown in Figure~\ref{fig:decisiontree}. More conservative cuts can
be applied to create pure, but not necessarily complete, samples. These are
useful for selecting galaxies exhibiting unique morphologies for individual
case studies.  Looser cuts can be applied to obtain samples with a higher level
of completeness, (but with a potential decrease on the overall purity). We
stress that the details of any selection process will vary based on the
particular science case.
